Proposed Solution

### 2017-01-23 CAV17/secs/motiv.tex
cav17: motivating examples

By invoking \app, the user can detect such a configuration error.
In particular, \app reports that {\tt recode.so} 
should appear before {\tt mysql.so}, as shown
below: \ennan{Mark, please update all the motivating examples'
output results according
to our newest version implementation.}

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    ORDERING ERROR: Expected "extension" "recode.so"
    BEFORE "extension" "mysql.so"
\end{lstlisting}

%TODO would be nice to have these as subsection or somehow be able to ref specific examples
\para{Example~2: Fine-grained value correlation error}
\label{ex:fine}
Our second misconfiguration example~\cite{correlation} 
comes from a discussion on StackOverflow.
The user has configured her MySQL as in the following:

@@

The user complains that her MySQL load was very high, 
causing the website's
response speed to be very slow.
In this case, {\tt key\_buffer\_size} is used by all the threads
cooperatively, while {\tt join\_buffer} and {\tt sort\_buffer} are 
created by each thread for private use; thus, the maximum amount
of used key buffer, \ie, {\tt key\_buffer\_size}, should be larger than 
{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
Clearly, in the above example, it does not hold, 
so this misconfiguration causes MySQL to load very slowly.

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    INTEGER RELATION ERROR:
    Expected "key_buffer_size" >= "max_connections" * "sort_buffer_size"
\end{lstlisting}

We can see that during the learning process not only do we learn simple statements that compare two values, 
but also we learn more complex correlations. We call these more complex relations fine-grained value correlations, and the errors
\emph{fine-grained value correlation errors}. 
This type of error is more sophisticated than the simple value correlation that some tools can detect~\cite{yin11anempirical, zhang14encore}.
A typical value correlation error
states that one entry's value should have a certain correlation with
another entry's value. For example, in MySQL,
the value of {\tt max\_connections} should be higher than
{\tt mysql.max\_persistent}.

Our tool can learn this simple correlation as well, but learning more complex properties requires a different 
approach to the learning 
process. We need to track several variables. It is not enough just to compare them, but we need to learn, as in this particular case, which
invariant must be preserved. It was pointed out by Xu {\em et al.}~\cite{xu15hey} that
detecting fine-grained value correlation errors 
is a much more challenging
task than the normal value correlation problem.
To the best of our knowledge, \app is the first tool that
is able to check such fine-grained value correlation problems.

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    MISSING KEYWORD ERROR: Expected "overlay" "ppolicy"
    in the same file: "include" "schema/ppolicy.schema"
\end{lstlisting}

\para{Example~4: Type errors} 
Many system performance problems are caused by 
assigning incorrect type of values to some key in configuration
files. Consider the following real-world misconfiguration file: 
a user tries to install MySQL and she needs to initiate the path
of the log information generated by MySQL.
This user puts the following assignment in her MySQL
configuration file:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    general_log = /var/log/mysql/mysql.log
\end{lstlisting}

Unbeknowest to this user, the entry ``general\_log'' should be an 
integer, not a string. In MySQL, there is another entry named
``general\_log\_file'' used to specify the log path.
With \app, this user can get the following result:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    TYPE ERROR: Expected a Int with P=1.0 for
    "general_log [mysql]"
\end{lstlisting}

>>>>

By invoking \app, the user can detect such a configuration error.
In particular, \app reports that {\tt recode.so} 
should appear before {\tt mysql.so}, as shown
below:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    ORDERING ERROR: Expected "extension=recode.so"
    BEFORE "extension=mysql.so"
\end{lstlisting}

%TODO would be nice to have these as subsection or somehow be able to ref specific examples
\para{Example~2: Fine-grained integer correlation error}
\label{ex:fine}
Our second misconfiguration example~\cite{correlation} 
comes from a discussion on StackOverflow.
The user has configured her MySQL as in the following:

@@

The user complains that her MySQL load was very high, 
causing the website's
response speed to be very slow.
In this case, {\tt key\_buffer\_size} is used by all the threads
cooperatively, while {\tt join\_buffer} and {\tt sort\_buffer} are 
created by each thread for private use; thus, {\tt key\_buffer\_size},
\ie, the maximum amount of used key buffer, should be larger than 
{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
In the above example, however, it does not hold.

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
  FINE GRAINED INTEGER RELATION ERROR:
  Expected "max_connections" * "sort_buffer_size"
               =< "key_buffer_size"
\end{lstlisting}

The above example is a complex integer correlation, which implicitly
includes a computational correlation among different entries
in the configuration file.
We call these complex integer correlations as 
{\em fine-grained integer correlations}. 
Our tool can detect simple integer correlation---one entry's
value should have a certain correlation with another entry's 
value---as well.
For example, in MySQL, the value of {\tt max\_connections} 
should be higher than {\tt mysql.max\_persistent}.
While few existing tools~\cite{yin11anempirical, zhang14encore}
can detect the simple integer correlation errors,
to the best of our knowledge, \app is the first effort capable of
detecting fine-grained integer correlation problems.

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    MISSING ENTRY ERROR: Expected "overlay" "ppolicy"
    in the same file: "include" "schema/ppolicy.schema"
\end{lstlisting}

\para{Example~4: Type errors} 
Many system availability problems are caused by 
assigning incorrect type of values to some key in configuration
files. Consider the following real-world misconfiguration
file~\cite{typeerror}: 
a user tries to install MySQL and she needs to initiate the path
of the log information generated by MySQL.
This user puts the following entry assignment in her MySQL
configuration file:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    slow-query-log = /var/log/mysql/slow.log
\end{lstlisting}

Unbeknowest to this user, the entry ``slow-query-log'' should be an 
integer, not a string. This misconfiguration will lead to 
MySQL fails to start~\cite{querylog}. In MySQL, there is another entry 
named ``slow-query-log-file'' used to specify the log path.
With \app, this user can get the following result:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    TYPE ERROR: Expected a Int with P=1.0 for
    "slow-query-log"
\end{lstlisting}
